%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventrytarget
    {Senior Software Engineer} % Job title
    {Software Engineer} % Job title
    {Target Corporation}
    {Minneapolis, MN} % Location
    {July 2022 - Current} % Date(s)
    {August 2021 - July 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and built an entirely new built from scratch Web Application enabling the bulk purchase of Gift Cards by business clients, facilitating over \$250 million in revenue}
        \item {Built UI's using Next.js, leveraging micro-frontend design patterns using Webpack Module Federation.}
        \item {Built API microservices using Micronaut and Kotlin.}
        \item {Deployed and maintained infrastructure for PCI compliant microservices in the Google Cloud using Terraform.}
        \item {Implemented and maintained secure deployment pipelines for a high risk UI micro-frontend that captures PCI data.}
        \item {Implemented monitoring integrations with InfluxDB, Grafana, Kibana, ShuttleIO, and Slack}
        \item {Implemented Oauth2 intergrations to handle authentication and authorization for external clients and internal team members}
        \item {Implemented cross team integrations using API's and Kafka Event Streaming.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full Stack Developer} % Job title
    {Lively Apps} % Organization
    {Vancouver, British Columbia} % Location
    {April 2020 - August 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and maintained apps currently available on the Atlassian marketplace for Confluence and Jira. Including Pocket Query, Task Reminder, Hide Elements, Lively Recorder, Usage Statistics for Confluence and more.}
        \item {Won second place in the 2020 Codegeist hackathon for the Lively Recorder.}
        \item {Implemented apps and features using the React framework for frontend and Java Spring for backend services}
        \item {Built and deployed overall service infrastructure utilizing Docker and AWS (Including EC2, Lambda, S3, and CloudFront), focusing on high-availability, fault tolerance, and auto-scaling.}
        \item {Solved support tickets, interacting directly with customers.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Teaching Assistant} % Job title
    {University of British Columbia} % Organization
    {Vancouver, Biritsh Columbia} % Location
    {January - August 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Taught Java language, design principals, and design patterns}
        \item {Assisted students in the design and development of capstone personal projects.}
        \item {Graded assignments, quizzes and exams}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Quality Assurance Intern} % Job title
    {Garmin} % Organization
    {Cochrane, Alberta} % Location
    {September - December 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Authored and maintained well organized, efficient and successful test cases for the entire team.}
        \item {Designed and built internal tools used to automate testing processes}
        \item {Debugged code and located root causes of problems by reviewing configuration files and logs}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
