%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventrytarget
    {Senior Software Engineer} % Job title
    {Software Engineer} % Job title
    {Target Corporation}
    {Minneapolis, MN} % Location
    {July 2022 - Current} % Date(s)
    {August 2021 - July 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and built an entirely new built from scratch e-commerce platform for the bulk purchase of Gift Cards by business clients, facilitating over \$250 million in revenue. This project went live in June 2024.}
        \item {Implemented UI's using Next.JS, React, Typescript, React Query, and Webpack.}
        \item {Developed a PCI compliant micro-frontend using Webpack Module Federation and deployed as a static javascript bundle to Google Cloud Platform.}
        \item {Designed and Implemented Frontend and Backend performance monitoring and alerting patterns to ensure our apps are up and performant at all times.}
        \item {Developed REST API microservices using Micronaut and Kotlin.}
        \item {Led the Production environment set up and production roll out effort. We had a clean production go live with no major incidents.}
        \item {Led the security development efforts including setting up frontend and backend controls to prevent known attack vectors. Prioritizing secure development from the beginning saved us time and resources when our PEN test resulted in no significant findings.}
        \item {Designed and built a Kafka filtering service that allowed the team to test our data migration in a "Go-Live" environment while ensuring that production PI data would not leak into lower environments.}
        \item {Supported the team through mentorship of Interns and Engineers.}
        \item {Developed two side project tools, git1s and git-history, that are used by engineers throughout Target Tech to more effectively use Github.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full Stack Developer} % Job title
    {Lively Apps} % Organization
    {Vancouver, British Columbia} % Location
    {April 2020 - August 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and maintained apps currently available on the Atlassian marketplace for Confluence and Jira. Including Pocket Query, Task Reminder, Hide Elements, Lively Recorder, Usage Statistics for Confluence and more.}
        \item {Won second place in the 2020 Codegeist hackathon for the Lively Recorder.}
        \item {Implemented apps and features using the React framework for frontend and Java Spring for backend services}
        \item {Developed and deployed overall service infrastructure utilizing Docker and AWS, focusing on high-availability, fault tolerance, and auto-scaling.}
        \item {Solved support tickets, interacting directly with customers.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Teaching Assistant} % Job title
    {University of British Columbia} % Organization
    {Vancouver, British Columbia} % Location
    {January - August 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Taught Java language, design principals, and design patterns}
        \item {Assisted students in the design and development of capstone personal projects.}
        \item {Graded assignments, quizzes and exams}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Quality Assurance Intern} % Job title
    {Garmin} % Organization
    {Cochrane, Alberta} % Location
    {September - December 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Authored and maintained well organized, efficient and successful test cases for the entire team.}
        \item {Designed and built internal tools used to automate testing processes}
        \item {Debugged code and located root causes of problems by reviewing configuration files and logs}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
